worldmap

### 2024-12-19 analysis/figures/visualization.Rmd
Save high quality figures.

ggsave(here::here("figures/study_map.jpeg"), bg = "white")
```

@@

ggsave2(here::here("figures/study_map_hist.jpeg"), bg = "white")
```

@@

plot_map <- tibble(metric_name = c("S", "Jaccard_base", "SES_FRic", "SES_FDiv", "SES_FEve"), 
           ylabel = c("log(S)", "log(Jaccard + 1)", "Functional Richness SES", "Functional Divergence SES", "Functional Evenness SES"),
           #ylabel = c("log(S)", "Jaccard", "Functional\nRichness SES", "Functional\nDivergence SES", "Functional\nEvenness SES"),
           yval = c("log(value)", "logvalue", "value", "value", "value"),
           xlabel = c(NA, NA, NA, "year", "year"))
m_plots <- pmap(plot_map, plot_metric, data = model_data %>% mutate("log(value)" = log(value)), 
                model_coef = metric_model_table %>% filter(model_id == "base"), 
                color_list = group_colors)

@@

ggsave2(here::here("figures", "3met_long.jpeg"), bg = "white")
```

@@

keep <- pmap(slope_plot_df %>% filter(metric_name == "CWM_diet_planto"), plot_slopes)
keep

@@

cowplot::save_plot(here::here("figures/slope_plot_grid_test.png"), slope_plot_grid, ncol = 7, nrow = 5, bg = "white", base_asp = .7)

@@

  duration_legend <- get_legend(duration_legend_plot)
  leg <- grid.arrange(duration_legend)
  ggsave(here::here(paste0("figures/slope_legends/", color, "_legend.png")), leg, width = .6, height = 1.5,
         bg = "transparent")
}

@@

contrasts_plot_grid <- climate_plot + taxa_plot + pa_plot + realm_plot + plot_layout(ncol = 4, axis_titles = "collect")
ggsave(here::here("figures/contrasts_plot_grid.png"), contrasts_plot_grid, width = 15, heigh = 6)
```

>>>>

ggsave(here::here("figures/study_map.jpeg"), bg = "white", dpi = 800)
```

@@

ggsave2(here::here("figures/study_map_hist.jpeg"), bg = "white", dpi = 1000, width = 180, units = "mm")
```

@@

plot_map <- tibble(metric_name = c("S", "Jaccard_base", "SES_FRic", "SES_FDiv", "SES_FEve"), 
           ylabel = c("log(S)", "log(Jaccard + 1)", "Functional Richness SES", "Functional Divergence SES", "Functional Evenness SES"),
           #ylabel = c("log(S)", "Jaccard", "Functional\nRichness SES", "Functional\nDivergence SES", "Functional\nEvenness SES"),
           yval = c("log(value)", "logvalue", "value", "value", "value"),
           xlabel = c(NA, NA, NA, "year", "year"))
m_plots <- pmap(plot_map, plot_metric, data = model_data %>% mutate("log(value)" = log(value)), 
                model_coef = metric_model_table %>% filter(model_id == "base"), 
                color_list = group_colors, 
                legend = FALSE)

@@

ggsave2(here::here("figures", "3met_long.jpeg"), bg = "white", width = 180, unit = "mm", dpi = 1000)
```

@@

@@

cowplot::save_plot(here::here("figures/slope_plot_grid_test.png"), slope_plot_grid, ncol = 7, nrow = 5, bg = "white", base_asp = .7, dpi = 1000)

@@

  duration_legend <- get_legend(duration_legend_plot)
  leg <- gridExtra::grid.arrange(duration_legend)
  ggsave(here::here(paste0("figures/slope_legends/", color, "_legend.png")), leg, width = .6, height = 1.5,
         bg = "transparent", dpi = 800)
}

@@

contrasts_plot_grid <- climate_plot + taxa_plot + pa_plot + realm_plot + plot_layout(ncol = 4, axis_titles = "collect")
ggsave(here::here("figures/contrasts_plot_grid.jpg"), contrasts_plot_grid, width = 15, heigh = 6, dpi = 1000)
```
